A Detection of the Environmental Dependence of the Stellar Halos of Massive Central Galaxies

### 2017-03-14 draft/ms.tex
New draft

% Version 0; preprint format; Written by SH

\documentclass[preprint]{aastex}
\usepackage{emulateapj5}
\usepackage{apjfonts}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{CJK}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\bibliographystyle{apj}

\input psfig.tex

@@

\newdimen\digitwidth    % These five lines change the meaning of
\setbox1=\hbox{0}       % " in the same way, so that it leaves as
\digitwidth=\wd1        % much space as a digit. (Note: All digits
\catcode`"=\active      % are the same width).

% Luis's Definitions
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def"{\kern\digitwidth}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\etal{{\ et al.~}}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\it HST}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\pp{\parshape 2 0truein 6.1truein .3truein 5.5truein}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\solum{$L_\odot$}
\def\solmass{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

%Song Huang's definition 
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}

@@

\slugcomment{Draft version 0}
\shorttitle{ENVIRONMENT DEPENDENCE OF MASS-SIZE RELATION}
\shortauthors{HUANG ET AL.}

@@

\begin{CJK*}{UTF8}{gbsn}

\title{The Environmental Dependence of Structures for Massive Galaxies
from the Hyper-Suprime Camera Survey}

\author{Song Huang (黄崧)\altaffilmark{1} Alexie Leauthaud\altaffilmark{1}, 
Kevin Bundy\altaffilmark{1}, and You}
\date{}

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
Universe, Todai Institutes for Advanced Study, the University of Tokyo (Kavli
IPMU, WPI), Kashiwa 277-8583, Japan}

@@

  Many recent observations and numerical simulations suggest that nearby
  massive, early-type galaxies are formed through a ``two-phase'' process.  In
  the proposed second phase, the extended stellar envelope was accumulated
  through many dry mergers. (XX TODO)

\end{abstract}
\keywords{galaxies: elliptical and lenticular, cD --- galaxies: formation --- 
          galaxies: photometry --- galaxies: structure --- galaxies: surveys}

@@

\section{Introduction}

\section{Sample and Data Reduction}

\section{Results}

\section{Discussion}

\section{Summary}

%%%%%%%%%%: Acknowledge %%%%%%%%%%

\acknowledgements

  1. Acknowledgements for HSC 
  2. Acknowledgements for Kevin and Alexie's funding 
  3. Acknowledgements for the Python libraries

  Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the
  Participating Institutions, the National Science Foundation, and the U.S.
  Department of Energy. The SDSS-III web site is http://www.sdss3.org.  SDSS-III
  is managed by the Astrophysical Research Consortium for the Participating
  Institutions of the SDSS-III Collaboration including the University of
  Arizona, the Brazilian Participation Group, Brookhaven National Laboratory,
  University of Cambridge, University of Florida, the French Participation
  Group, the German Participation Group, the Instituto de Astrofisica de
  Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns
  Hopkins University, Lawrence Berkeley National Laboratory, Max Planck
  Institute for Astrophysics, New Mexico State University, New York University,
  Ohio State University, Pennsylvania State University, University of
  Portsmouth, Princeton University, the Spanish Participation Group, University
  of Tokyo, University of Utah, Vanderbilt University, University of Virginia,
  University of Washington, and Yale University.

%%%%%%%%%%: Bibligraphic Section %%%%%%%%%%

%\begin{thebibliography}{}

  %\bibitem[Arnold et al.(2011)]{2011ApJ...736L..26A} Arnold, J.~A., Romanowsky,
    %A.~J., Brodie, J.~P., et al.\ 2011, \apjl, 736, LL26

%\end{thebibliography}{}

\bibliography{redbcg}

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH

\documentclass[a4paper,fleqn,usenatbib]{mnras}

% Packages
%\usepackage{deluxetable}
%\usepackage{apjfonts}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage[usenames, dvipsnames]{color}

% Package Settings
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}

% Figure extention
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

@@

% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\aa{{A\&A}}
\def\aas{{ A\&AS}}
\def\aj{{AJ}}
\def\al{$\alpha$}
\def\bet{$\beta$}
\def\amin{$^\prime$}
\def\annrev{{ARA\&A}}
\def\apj{{ApJ}}
\def\apjs{{ApJS}}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\cc{cm$^{-3}$}
\def\flamb{erg s$^{-1}$ cm$^{-2}$ \AA$^{-1}$}
\def\flux{erg s$^{-1}$ cm$^{-2}$}
\def\fnu{erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$}
\def\hst{{\textit{HST}}}
\def\kms{km s$^{-1}$}
\def\lamb{$\lambda$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\mnras{{MNRAS}}
\def\nat{{Nature}}
\def\pasp{{PASP}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\reference{\noindent\pp}
\def\refindent{\par\noindent\parskip=2pt\hangindent=3pc\hangafter=1 }
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$} 
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}
\newcommand{\lt}{<}
\newcommand{\gt}{>}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}}
\def\cmodel{\texttt{cModel}}
% Samples
\def\rbcg{\texttt{cenHighMh}}
\def\nbcg{\texttt{cenLowMh}}
\def\redbcg{{$\lambda \ge 30$}}
\def\nonbcg{{$\lambda < 20$}}
% Mass related 
\def\mstar{{$M_{\star}$}}
\def\mhalo{{$M_{\mathrm{halo}}$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}}

\def\minn{{$M_{\star,10\mathrm{kpc}}$}}
\def\meff{{$M_{\star,15\mathrm{kpc}}$}} 
\def\mtot{{$M_{\star,100\mathrm{kpc}}$}}
\def\mout{{$M_{\star,150\mathrm{kpc}}$}}
\def\mmax{{$M_{\star,\mathrm{Max}}$}}
\def\mgama{{$M_{\star,\mathrm{GAMA}}$}}
\def\mcmodel{{$M_{\star,\mathrm{cModel}}$}}

\def\logminn{{$\log (M_{\star,10\mathrm{kpc}}/M_{\odot})$}}
\def\logmtot{{$\log (M_{\star,100\mathrm{kpc}}/M_{\odot})$}}
\def\logmout{{$\log (M_{\star,150\mathrm{kpc}}/M_{\odot})$}}
\def\logmmax{{$\log (M_{\star,\mathrm{Max}}/M_{\odot})$}}
\def\logmgama{{$\log (M_{\star,\mathrm{GAMA}}/M_{\odot})$}}
\def\logmcmodel{{$\log (M_{\star,\mathrm{cModel}}/M_{\odot})$}}

\def\m2l{{$M_{\star}/L_{\star}$}}
\def\mden{{$\mu_{\star}$}}

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
%\newcommand{\update}[1]{#1}

\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Halos of Massive Central Galaxies}

\author[S. Huang et al.]{Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        HSC collaboration$^{3}$   
        \\ \\
        % List of institutions
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }

\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

%        \author{Song Huang\altaffilmark{1} 
%        Alexie Leauthaud\altaffilmark{1}, 
%        Kevin Bundy\altaffilmark{1},
%        Michael Strauss\altaffilmark{2},
%        Yen-Ting Lin\altaffilmark{3},
%        Rachel Mandelbaum\altaffilmark{4}
%        }
%\altaffiltext{2}{Princeton University Observatory, 
%    Peyton Hall, Princeton, NJ 08544, USA}
%\altaffiltext{3}{Institute of Astronomy and Astrophysics, Academia Sinica, 
%    P.O.~Box 23--141, Taipei 10617, Taiwan}
%\altaffiltext{4}{Carnegie-Mellon University \todo{correct affiliation here}}

@@

@@

\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}

@@

    The promising hierarchical assembly scenario of massive galaxies suggest the 
    structure of these galaxies should depend on their environments or halo mass.
    Yet, at low redshift, observations find no clear evidence for that. 
    Here, using the deep images from the Subaru Hyper Suprime-Cam (HSC) survey,
    we map the stellar mass distributions of massive galaxies at $0.3 < z < 0.5$ 
    out to the very outskirt, and detect subtle, but robust structural differences 
    that depend on halo mass for central galaxies at high mass end. 
    With the help of the \redm{} catalog, we separate these massive galaxies 
    into centrals of halos that are more and less massive than 
    $M_{200m}\sim 10^{14} M_{\odot}$.
    For centrals with similar stellar mass within 100 kpc, the ones from 
    more massive halos on average have slightly more flattened inner profile 
    within $\sim 10$-$20$ kpc, and more prominent outer envelope.
    Meanwhile, when matched at the same stellar mass within inner 10 kpc--a 
    proxy of the mass of the in-situ component, the massive centrals of more  
    massive halos show much more significant outer stellar envelopes.    
    We also see that these two samples of massive galaxies follow slightly 
    different mass-size relation and the relationship between the stellar mass 
    within 100 and 10 kpc.
    Such differences in structure are broadly consistent with the expectation that
    central galaxy from more massive halo should have more complex merging history.
    These results highlight the importance of deep photometry in the study of 
    the assembly history of massive galaxies.

\end{abstract}

\begin{keywords}
    galaxies: elliptical and lenticular, cD --
    galaxies: formation --
    galaxies: photometry -- 
    galaxies: structure -- 
    galaxies: surveys}
\end{keywords}

@@

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_sdss_compare}
        \caption{
            A comparison between the imaging quality of SDSS and HSC Wide for a sample 
        	of nearby massive elliptical galaxies at $0.2 < z < 0.5$.  
            These images are generated using $gri$ band images with an arcsinh stretch 
            \citep{Lupton2004}. 
            The HSC \texttt{WIDE} layer is $3.0$-$4.0$ magnitudes deeper than SDSS 
            which is critical to map the outskirts of ETGs out to large radii.
            }
        \label{fig:sdss_compare}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z\sim 0.4$, and 
          with similar values for their \mstar{} within a 10 kpc aperture 
          (the dash-line circle on top-left figure indicates the scale of 10 kpc;
          $11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed "inner" mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          $\sim 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}
    \label{sec:intro}

    Massive galaxies are unique laboratories to study both cosmology and galaxy 
    formation. 
    Although the hierarchical growth scenario under the $\Lambda$-CDM cosmology 
    is a solid theoretical background (e.g. \citealt{Baugh1996, DeLucia2006}, 
    plenty important questions regarding the star-formation history, mass assembly 
    process, and structural evolution of these massive galaxies remain open. 
    Thanks to the advances in observations and numerical simulations, the newly 
    developed ``two-phase'' formation scenario (e.g. \citealt{Oser2010, Oser2012}) 
    becomes the most promising theory that can reasonably explain different 
    observations of massive galaxies. 
    Under this picture, the highly dissipative processes at high-$z$ (e.g cold 
    accretion, gas-rich merger; e.g. \citealt{Hopkins2008, Dekel2009}) induce 
    intense starburst, and quickly form the massive progenitors of $z\sim 0$ massive 
    early-type galaxies (ETGs).     
    Later, certain physical mechanism (e.g. AGN feedback; e.g. \citealt{Sijacki2007,
    Fabian2012}) 
    efficiently quenched the on-going star formation so that a large fraction of 
    these massive progenitors become quiescent at $z>1$ (e.g. \citealt{Bezanson2009,
    Kriek2016}). 
    At the same stellar mass (\mstar{}), these so-called ``red nuggets'' 
    (e.g. \citealt{Damjanov2009}) have smaller effective radius 
    ($R_{\mathrm{e}}$; \citealt{Trujillo2006, vanDokkum2008, Cimatti2008}), 
    slightly higher central velocity dispersion and stellar mass density 
    (\mden{}; e.g. \citealt{vandeSande2011, Belli2014}), more disk-like morphology 
    (e.g. \citealt{vanderWel2011}) than their local descendants 
    (e.g. \citealt{Bezanson2009, vanDokkum2010}). 
    Later, the second phase of evolution is driven by non-dissipative processes 
    like dry mergers with other galaxies (e.g. \citealt{Naab2006, Khochfar2006}). 
    According to the ``two-phase'' scenario, minor mergers make dominated 
    contribution during this period as they help explain the significant increase
    of $R_{\mathrm{e}}$ (e.g. \citealt{Newman2012, vdWel2014}) and accumulation of 
    outer stellar halo (e.g.  \citealt{Szomoru2012, Patel2013}).

    Despite the great success, it also raises new questions. 
    Under the $\Lambda$-CDM cosmology, the formation of galaxy is intrinsically 
    tied to the growth of the host dark matter halo 
    (e.g. \citealt{Leauthaud2012, Behroozi2013}).
    Massive ETGs living in the center of more massive halos should experience 
    different mass assembly history and undergo different merging events comparing 
    to the ones from smaller halos. 
    Therefore, it is reasonable to expect that the structures of massive galaxies
    depend on the ``environment''\footnote{Although there are different 
    observational definition of environment, we use the term ``environment'' and 
    halo mass interchangeably in this work.}.

    As one of the most important structural parameters, the $R_{\mathrm{e}}$ of 
    massive ETGs follows a tight and steep relation with the \mstar{} 
    (e.g. \citealt{Shen2003, Guo2009}). 
    Models based on the ``two-phase'' formation scenario naturally predict that 
    such mass--size relation should show environmental dependence, and 
    $R_{\mathrm{e}}$ of massive ETGs in more massive halos should be larger 
    than the ones in less massive halos at fixed \mstar{} 
    (e.g. \citealt{Shankar2013, Shankar2014}). 
    Interestingly, while hints of such dependence have been spotted at high-$z$ 
    (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but also see 
    \citealt{Rettura2010}), solid evidence of it at low-$z$ is still absence 
    (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}).
    This confusing result becomes a challenge to the hierarchical growth model 
    of massive galaxies. 
    On the observational side, both the depth of the images and the photometric 
    method contribute to this problem. 
    The steep inner \mden{} profiles, extremely extended stellar envelopes, 
    and other structural details make it very difficult to accurately define and 
    measure the \mstar{} and $R_{\mathrm{e}}$ of massive ETGs 
    (e.g. \citealt{Bernardi2013, DSouza2014}).

    Here, taking advantage of the excellent image quality of the HSC survey, we 
    investigate the environmental dependence of structure in massive galaxies 
    via comparing the \mden{} profiles and structural scaling relations between 
    massive central galaxies living in more and less massive dark matter halos. 
    Both the deep imaging depth ($i$-band images are typically 3-4 magnitude deeper 
    than SDSS ones) and the good seeing condition (median FWHM$\sim 0.6^{\arcsec}$
    in $i$-band) of the HSC images make them perfect for mapping the \mstar{}
    distributions of massive galaxies out to very large radius (see 
    Fig~\ref{fig:sdss_compare}). 
    With the help of a cluster catalog, we select a large sample of massive central 
    galaxies in halos that are more or less massive than \logmh{}$\sim 14.0$ at 
    $0.3 < z < 0.5$ from the available $\sim 100$ square degree of HSC data.

    Motivated by the ``two-phase'' scenario, also due to the difficulty in 
    appropriately modeling the \mstar{} distributions of massive galaxies out to 
    their very outskirts, we focus on \mstar{} within two different physical apertures 
    in this work:

    \begin{itemize}
        \item \mstar{} within 10 kpc, \minn{}: according to the ``two-phase'' 
            scenario, the ``in-situ'' star-formation quickly built up the inner, dense 
            core of massive ETGs.  
            Based on recent observations and simulations (e.g.~\citealt{vanDokkum2010}; 
            \citealt{RodriguezGomez2016}), the in-situ 
            component distributes mostly within the effect radius ($R_{\mathrm{e}}$, 
            or 5-10 kpc) in massive galaxies.  
            Here we use \minn{} as a proxy of the \mstar{} formed in the ``in-situ''
            phase.  Although it is an empirical choice, the detailed comparison of 
            the stellar mass surface density (\mden{}) profiles later suggests it indeed 
            helps reveal interesting environmental dependence.  
            Under the adopted cosmology, $1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshift 0.3 and 0.5.  
            We can reliably measure \minn{} without being bothered by smearing effect
            of seeing.
        \item \mstar{} within 100 kpc, \mtot{}: for massive galaxies in this work, 
            100 kpc aperture reaches to 5-10 $\times R_{\mathrm{e}}$ and very low 
            \mden{} region, hence can be treated as proxy of the ``total'' \mstar{}. 
            Limited by the accuracy of background subtraction, the \mden{} profile 
            of outer region can not be reliably recovered for massive galaxies across 
            our redshift range. 
            Although not perfect, \mtot{} is still a much better tracer of total 
            \mstar{} than the model-dependent ones using shallower images.
    \end{itemize}

    Massive central galaxies in this work show an intriguing diversity on the 
    plane defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z\sim 0.4$ that share very similar value of \minn{}, but show 
    a large range of outer structures. 
    Assuming galaxies at the same \minn{} have similar amount stars in the in-situ 
    component, it is of great interest to investigate the relation between their 
    environments and outer envelopes that are assembled at later time. 
    It is worth noting that, although a circular aperture is shown on 
    Fig~\ref{fig:m100_m10_color}, we always use elliptical apertures that follow the 
    average isophotal shape for photometry in this work.
    And, within our choices of redshift and \mstar{} ranges, we can safely ignore 
    significant mass growth and structural evolution 
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}) 
    with our redshift and \mstar{} ranges.

    The paper is organized as follows. Section\ref{sec:data} gives a brief overview of 
    the HSC observation and data reduction, along with the summary of the data selection
    processes.  
    Then, we will explain the procedures for extracting 1-D surface brightness profiles 
    (Section \ref{sec:ellipse}) and estimating stellar mass (Section \ref{sec:mstar}) in
    details.   
    We will present the main results in Section \ref{sec:result}, and discuss the several 
    related technical and scientific issues in Section \ref{sec:discussion}, ending with
    summary and future plans in Section \ref{sec:summary}.

    All the magnitudes used here are in AB system (\citealt{Oke1983}), and are corrected 
    for Galactic extinction using calibrations from \citet{Schlafly11}.
    In this work, we assume $H_0$ = 70~km~s$^{-1}$ Mpc$^{-1}$, ${\Omega}_m=0.3$, 
    and ${\Omega}_{\lambda}=0.7$.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. 
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure. 
            The dash-line shows the surface brightness profile after correcting the 
            background. 
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            affected by seeing. 
            The grey shaded region highlights the region most affect by seeing 
            ($r<3$ kpc).
            On the top panel, the dash line shows the ellipticity used for the final 
            isophote. 
            Right: the masked $i$-band image of this galaxy with the isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}\sim 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Data And Sample Selection}
    \label{sec:data}

\subsection{The Hyper Suprime-Cam Survey}
    \label{ssec:hsc}

    The Subaru Strategic Program (SSP, \citealt{MiyazakiInPrep}) makes use of the new 
    prime-focus camera, the Hyper Suprime-Cam (HSC;~\citealt{Miyazaki2012}), on the 
    8.2-m Subaru telescope at Mauna Kea. 
    The ambitious multi-layer HSC survey takes advantage of the large field of 
    view (FoV;~1.5 deg in diameter) of this camera and will cover $\sim 1400$ deg$^2$ 
    in 5 broad bands (\textit{g r i z Y}) to a limiting depth of $r \sim 26$ mag 
    in the \texttt{WIDE} layer. 
    This work is based on the internal data release \texttt{S15B}, which covers 
    $\sim 100$ deg$^2$ in all 5-band to full \texttt{WIDE} depth.  
    The regions covered by this release overlap with a number of spectroscopic surveys 
    (e.g.\ SDSS/BOSS: \citealt{Eisenstein2011}, \citealt{Alam2015}; 
    GAMA: \citealt{Driver2011}, \citealt{Liske2015}).

    The HSC \texttt{WIDE} survey is about $3.0$-$4.0$ magnitudes deeper in the $i$-band 
    than SDSS. 
    Combined with the excellent imaging resolution (the median $i$-band seeing is 0.6"), 
    and the wide area, the HSC survey represents a tremendous data set to perform a 
    large statistical study of the surface brightness profiles of ETGs out to large radii.     
    Fig~\ref{fig:sdss_compare} illustrates the quality of HSC imaging compared to SDSS 
    for three low redshift ETGs, and shows that HSC survey data are well suited for 
    mapping the stellar distribution of massive galaxies out to large radii.

	HSC $i$-band images typically have the best seeing compared to other bands because 
	of strict requirements driven by weak lensing science. 
    We will therefore use the $i$-band images to measure the stellar distributions of 
    massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{HSC Data Processing}
    \label{sec:pipeline}

    The full details of the HSC data processing can be found in \citet{BoschInPrep}
    and are briefly summarized here. 
    The HSC SSP data are processed with \texttt{hscPipe 4.0.1}, a derivative of the 
    Large Synoptic Survey Telescope (LSST) pipeline (e.g.\ \citealt{Juric2015}; 
    \citealt{Axelrod2010}), modified for HSC. 
    \texttt{hscPipe} first performs a number of tasks at the single exposure level 
    (bias subtraction, flat fielding, background modeling, object detection and 
    measurements). 
    Astrometric and photometric calibrations are performed at the single exposure level. 
    \texttt{hscPipe} then warps different exposures on to a common World Coordinate 
    System (WCS) and combines them into coadded images. 
    At this stage, \texttt{hscPipe} updates the images with a better astrometric and 
    photometric calibration using stars that are common among exposures.

    The pixel scale of the combined images is $0.168^{\arcsec}$. 
    Photometric calibration is based on data from the Panoramic Survey Telescope 
    and Rapid Response System (Pan-STARRS) 1 imaging survey 
    (\citealt{Schlafly2012}, \citealt{Tonry2012}, \citealt{Magnier2013}). 
    To achieve consistent deblending and photometry across all bands, \texttt{hscPipe} 
    performs multi-band post-processing at the coadd level. 
    First, \texttt{hscPipe} performs object detection on coadd images in each band 
    independently and records the flux peak and the above-threshold region 
    (referred as a ``footprint'') for each source. 
    Next, ``footprints'' and peaks from different bands are merged together before     
    performing deblending and measurements. 
    Finally, \texttt{hscPipe} selects a reference band for each object based on the 
    $S/N$ in different bands (for most galaxies in this work, the reference band is 
    the $i$-band). 
    After fixing the centroids, shape, and other non-amplitude parameters of each 
    object in this reference catalog, \texttt{hscPipe} perform forced photometry 
    on the coadd image in each band. 
    This forced photometry approach is optimized to yield accurate galaxy colors.

    For each galaxy, \texttt{hscPipe} measures a \cmodel{} magnitude using an approach 
    that is similar to SDSS (\citealt{BoschInPrep}). 
    However, as opposed to SDSS, the HSC \cmodel{} is based on forced photometry which 
    means that it can accurately measure both the \textit{fluxes and colors of galaxies}. 
    The HSC \cmodel{} algorithm fits the flux distribution of each object using a 
    combination of a de~Vaucouleur and an exponential component and accounts for the PSF. 
    The performance of this algorithm has been tested using synthetic objects 
    (\citealt{SynPipeInPrep}), and the results indicate that, generally speaking, 
    the HSC \cmodel{} photometry is accurate down to $i >25.0$ mag.  
    However, \cmodel{} currently systematically underestimates the total fluxes of 
    massive ETGs with extended stellar distributions. 
    This is caused by an intrinsic limitation of \cmodel{} as it is incapable of
    modeling profiles with extremely extended outskirts, a problem that is exacerbated 
    at the depth of the HSC survey. 
    In addition, at the depth of the HSC survey, accurate deblending in the vicinity of
    large ETGs where satellites and background galaxies often blend with the low surface 
    brightness stellar envelope is a challenging problem. 
    The deblending method implemented by the \texttt{hscPipe} currently tends to 
    ``over-deblend'' the outskirts of bright galaxies and leads to un 
    under-estimation of the the total flux of massive ETGs (more discussion in 
    \citealt{BoschInPrep}).  
    For these reasons, our results will be based on custom developed code to measure 
    the luminosities and stellar masses of massive galaxies. 
    We use the HSC \texttt{hscPipe} photometry for two purposes: 
    1) to perform a first broad sample selection, and 2) to estimate the average 
    color of massive galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Initial Massive Galaxy Sample}
    \label{ssec:initial}

    We begin by using a broad luminosity cut to select an initial sample of massive 
    galaxies at $z < 0.5$ from the HSC photometric catalog. 
    Based on Leauthaud\etal~(2016), galaxies with \logms{}$\geq 11.5$ mostly have 
    $i_{\mathrm{SDSS, cModel}} \leq 21.0$ mag. 
    We therefore select our initial sample to be brighter than 
    $i_{\mathrm{HSC, cModel}} \leq 21.5$\footnote{We neglect the insignificant 
    differences between the response curves of SDSS-$i$ and HSC-$i$ filters} 
    and also limit our sample to regions that have reached the required depth of 
    the \texttt{WIDE} survey in $i$-band.
    %% The SQL search is saved as "sample.sql" 
    %% The master catalog used here is "dr1_wide_galaxy_icmodel_21.5.fits"
    %%   The original catalogs contain 2275477 objects

    We further select extended objects with no deblending errors, with well defined 
    centroids, and with \texttt{cModel} magnitudes in all five bands. 
    After removing objects that have pixels affected by saturation, cosmic-rays, or 
    other optical artifacts\footnote{each criterion removes less than 8\% of the 
    entire sample}
    %% Alexie: Actually, 8 percent is not small if we want to consider the number 
    %%         densities. Let's re-evaluate the impact of these cuts for the 16B 
    %%         data with FDFC}. 
    This sample corresponds to 1760845 galaxies and will be referred as \texttt{hscPho}. 
    %% Saved as "dr1_wide_galaxy_hscPho.fits"

    Here we limit our study to the very high-\mstar{} end where the majority of galaxies 
    have either a spectroscopic redshift or a robust red-sequence photo-$z$ from the 
    \redm{} catalog (see Section \ref{ssec:redmapper}).  
    We match the \texttt{hscPho} sample with a spec-$z$ catalog compiled by the HSC 
    team\footnote{It is created by matching HSC objects with all publicly available 
    spectroscopic redshifts (e.g.\ SDSS/BOSS; GAMA). The spec-z quality flag from 
    different catalogs are homogenized into a single flag that indicates whether the 
    redshift is secure (\ref{}). 
    We only consider the ones with secure spec-$z$s during the match}.  
    To ensure reasonable \mstar{}-completeness at the high-\mstar{} end we focus on
    the redshift range $0.3 \leq z \leq 0.5$. 
    %% This is catalog: "dr1_specz_use.fits"

    For objects without external spec-$z$, we match them with the central galaxies 
    from the \redm{} catalog using $2.0^{\arcsec}$ radius. 
    The matched objects with useful red-sequence photo-$z$ ($z_{\lambda}$) are also 
    included in the final sample of bright galaxies with reliable redshift between 
    $0.3 \leq z \leq 0.5$. 
    Comparing with spec-$z$, the accuracy of the red-sequence photo-$z$ is sufficient 
    (median $|z_{\lambda} - z_{\mathrm{Spec}}| \sim 0.01$ for the ones with spec-$z$) 
    for the goal of this work.
    The \redm{} catalog provides additional 133 unique redshifts for massive galaxies 
    in our sample.
    %% Estimated from "dr1_redbcg_hsc_sdss_gama_1arcsec.fits"
